---
title: "Activity Nine - Lab9"
author: "Taehoon Ha"
date: 11/7/2018
output: 
    github_document:
        toc: true
        toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(microbenchmark)
library(profvis)
```

### Question 1:
Consider a function that counts number of odd numbers in a given vector.

```{r}
odd_count <- function(x) {
    odd_num <- 0
    for (i in 1:length(x)) {
        if (x[i]%%2 == 1) 
            odd_num <- odd_num + 1
    }
    return(odd_num)
}
```

```{r}
odd_count2 <- function(x) {
    odd_num <- sum(x %% 2 != 0)
    return(odd_num)
}
```

<br>

Write a vectorized form of this function and compare their performance using **`microbenchmark` function** from the package `microbenchmark`.

```{r}
microbenchmark(odd_count(1:100), odd_count2(1:100), times = 100)
```

<br><br>

### Question 2: 
Create a matrix and calculate sum of each column:
+ using loop
+ using `apply()` function
+ using `colSums()` function

```{r}
(mat <- matrix(1:12, ncol = 3))

# using loop
matrix_sum <- function(mat) {
    matsum <- c(0,0,0)
    for (j in 1:ncol(mat)) {
        for (i in 1:nrow(mat)) {
            matsum[j] <- matsum[j] + mat[i,j]
        }
    }
    matsum
}
matrix_sum(mat)

# using `apply()` function
apply(mat, 2, sum)

# using `colSums()` function
colSums(mat)
```

<br>

Compare performance of the functions using `microbenchmark()` function.
```{r}
n <- 1:100
microbenchmark(matrix_sum(mat),
               apply(mat, 2, sum),
               colSums(mat), times = 100)
```

<br><br>

### Question 3: 
Create a random vector of positive integers of length 1,000,000 elements. Use `profvis()` function to profile the `odd_count()` function defined in the problem 1 with the vector as an input.

```{r eval = F}
profvis({
    dat <- sample(1:100, 1000000, replace = T)
    odd_count(dat)
    })
```

<p align="center">
<img src = 'https://ws2.sinaimg.cn/large/006tNbRwly1fx7nb72zvzj31hi0wm0zx.jpg'>
</p>
<br>
